\stktokens{}: Enforcing Well-bracketed Control Flow and Stack Encapsulation using Linear Capabilities

### 2018-07-05 fully-abstract-comp/popl2019/paper.tex
note for source machine section.

\begin{itemize}
\item present our source language, its operational semantics (excerpts)
\item mention our assumption of reasonability
\item present the full abstraction theorem.
\end{itemize}

@@

>>>>

\begin{itemize}
\item present our source language, its operational semantics (excerpts)
\item tell more about components, specifically well-formed according to judgement
\item mention our assumption of reasonability
\item present the full abstraction theorem.
\end{itemize}

@@

\begin{figure}
  \centering
  \begin{tikzpicture}[scale=0.8,every node/.style={scale=.9}]
    % \draw[help lines,yellow] (0,0) grid (10,7);
    \node at (5,4.7) { ${\src{C_1}\mathrel{\sconeq} \src{C_2}}$ };

    \node at (3.4,4) { ${\plug{\trg{\context}}{\src{C_1}} \sterm[]{\gc}{}}$ };
    \node at (5,4) { $\mathrel{\Rightarrow}$ };
    \node at (6.6,4) { ${\plug{\trg{\context}}{\src{C_2}} \sterm[]{\gc}{}}$ };

    \node at (4.35,2.8) { (1) };
    \node at (5,3.6) { (2) };
    \node at (5.65,2.8) { (3) };

    \draw[out=100,in=260,double,-implies,double equal sign distance] (4,2.6) to (4,3.4);

    \draw[out=280,in=80,double,-implies,double equal sign distance] (6,3.4) to (6,2.6);

    \node[align=left] at (8.2,3) { $ {\trg{\context}} \cong \trg{\context}$ \\
      $ {\src{C_2}} \cong \comp{{\src{C_2}}}$};
    \node[align=left] at (1.8,3) { $ {\trg{\context}} \cong \trg{\context}$ \\
      $ {\src{C_1}} \cong \comp{{\src{C_1}}}$};
    % \node at (9,2.7) { $e  {\src{C_1}} \cong \comp{{\src{C_1}}} : tau$ };
    % \node at (8.7,3.3) { $ {\comp{\trg{\context}}} \cong \trg{\context} :{\emptyset},tau \ra e,{\cdots}$ };
    % \node at (.8,3) { $e  {\src{C_1}} \cong \comp{{\src{C_1}}} : tau$ };

    \node at (3.4,2) { ${\plug{\trg{\context}}{\src{C_1}} \term[]{}}$ };
    \node at (5,2.1) { $\overset{?}{\Rightarrow}$ };
    \node at (6.6,2) { ${\plug{\trg{\context}}{\src{C_2}} \term[]{}}$ };

    \node at (5,1.3) { ${\src{C_1}}\mathrel{\overset{?}{\tconeq}}{\src{C_2}}$ };

    \draw[out=-90,in=90,double,-implies,double equal sign distance] (0,5) to node[sloped, yshift =.7em]{\small Contextual equivalence preservation} (0,1);
  \end{tikzpicture}
  \caption{Proving one direction of fully abstract compilation (contextual equivalence preservation).}
\end{figure}
